---
title: "Samsung Galaxy S Smartphone dataset CookBook"
output: html_document
---

## Merge Test/Train data sets

In this steps require merge available dataset in

1. test/X_test.txt
2. train/X_train.txt.

This test and training data set contains various statistics mean, std-dev and other attributes defined as 

1. tBodyAcc-mean()-X
2. tBodyAcc-mean()-Y
3. tBodyAcc-mean()-Z
4. tBodyAcc-std()-X
5. tBodyAcc-std()-Y
6. tBodyAcc-std()-Z
7. tBodyAcc-mad()-X
8. tBodyAcc-mad()-Y
9. tBodyAcc-mad()-Z
10. tBodyAcc-max()-X
11. tBodyAcc-max()-Y
12. tBodyAcc-max()-Z
13. tBodyAcc-min()-X
14. tBodyAcc-min()-Y
15. tBodyAcc-min()-Z
16. tBodyAcc-sma()
17. tBodyAcc-energy()-X
18. tBodyAcc-energy()-Y
19. tBodyAcc-energy()-Z
20. tBodyAcc-iqr()-X
21. tBodyAcc-iqr()-Y
22. tBodyAcc-iqr()-Z


```{r echo=FALSE, message=FALSE}
library(dplyr)

testdf<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/test/X_test.txt")
traindf<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/train/X_train.txt")
mdf<-rbind(testdf, traindf)
rm(testdf, traindf)
```

```{r echo=FALSE}
head(mdf)[1:2, 1:8]
```

## Associate meaning to dataset

Each column represent either mean, std-dev. 

1. features.txt

Represent each column. As part of data-wrangling it's very important to associate each column to appropriate meaningful value as represent in the file.

```{r echo=FALSE, message=FALSE}
  # Get Column Name
  col_name<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/features.txt")[,2]
  colnames(mdf)<-col_name
  mean_std=grepl("-(mean|std)\\()", col_name)
  mdf<-subset(mdf, select=mean_std)
  head(mdf)[1:2, 1:8]
```

## Activities

There are various activities defined in activity_labels.txt

1. WALKING
2. WALKING_UPSTAIRS
3. WALKING_DOWNSTAIRS
4. SITTING
5. STANDING
6. LAYING

Next steps require merging the activities training and test dataset into one merge data set.
Train and Test activities datasets are in

1. test/y_test.txt
2. trainy_train.txt

```{r echo=FALSE, message=FALSE}
  testdf<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/test/y_test.txt")
  traindf<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/train/y_train.txt")
  adf<-rbind(testdf, traindf)[,1]
  rm(testdf, traindf)
  head(adf)
```

# Translate Activities

```{r echo=FALSE, message=FALSE}
    activity_label<-read.table("~/datascience/springboard/datawrangling/exercise3/UCI/activity_labels.txt")[,2]
    ndf<-activity_label[adf]
    mdf<-cbind(Activities=ndf, mdf)
    rm(adf, ndf)
    head(mdf)[1:5, 1:6]
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Summary of project

```{r echo=FALSE, message=FALSE}
result<-mdf %>%
  group_by(Activities) %>%
  summarise_each(funs(mean))
head(result)[1:10, 1:6]
```

