---
title: "Movie Modeling"
output: html_document
---


## Overview
This data science project intent to analysize movies trends from available dataset  
available from last 100+ years.

Asking appropriate question or performing EDA (Exploratory Data Analysis) with the  
available dataset will help answer various trends in the past, present and probable   
future trends.

We expect that we will able to produce/answer following answer with the available  
dataset that will be of great help to the target audience.

We are asking the following question with the available dataset  

* What's has been the trend of Movie Genre being made in last 100+ yrs ?
* What's has been the production budget trend ?
* What's has been the production budget per Genre ?
* What's has been the domestic box office collection ?
* What's type of genre tend to maximize profit for production houses ?
* What's month of year sees minimum/maximum movie releases ?


### Target Audience 

This exploratory study is intent to target focus group who are related to entertainment
industry. 

1. Production Houses
    + Disney
    + Universal Studio
2. Entertainment Media Industry
    + Film Magzines.
    + Film Critics.
3. New entrepreneur to the Movie Industry.
4. Theatre Owner.

Individual client can see ongoing trends and apply predictive analysis with answer  
available for the above question. With the limited budget available for each production  
houses, better and wise decision can be made to fund genre to maximize profit.

Theater Owner can better decide on leasing theater space as volume of movie release  
varies for each month.

Film Critics/Film Magzines can analyzes further with changing times how the taste of  
audience have occurred and can be a dataset for other datascience studies being done  
for behaviour changes occuring in the society.

### Data Acquisition
We will acquire the data from http://www.the-numbers.com/movies. The webcrawler  
will acquire the dataset for each year and perform DataWrangling and present it
as a single source dataset.

Release Date | Movie       | Genre   | Production Budget | Domestic BoxOffice To Date
-------------|-------------|---------|-------------------|---------------------------
September 5  | Intolerance |Adventure| $200,000          | $8,000,000
December 31  | The Cabinet of Dr. Caligari| Horror | $150,000 | $300,000 

There are source for data acquisition and with project webcrawler can be extend for   other sources and data wrangling process can mitigate/resolve difference appropriately.

### Deliverables
This project will include R code and will be posted here 
**[github.com](https://github.com/mohankri/datascience/tree/master/springboard/project)**

It will also include result html (using R-markdown) have answer to the problem  
stated above.

Deliverables will include complete dataset, webCrawler for performing any update
of dataset.

```{r echo=FALSE, message=FALSE}
  DIR <- "~/datascience/springboard/project/"
  setwd(DIR)
  file<-list.files(paste(DIR, "./csv_files/",sep=""))
```

### Goal
The Goal is to model prediction for the following

1. Number of movies to be made in each individual genre. 
2. Production Budget Trend
3. Domestic Box-Office Collection Trend.


```{r echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(lattice)
library(devtools)
library(statisticalModeling)
library(rpart)
DIR<-paste(Sys.getenv("HOME"), "/datascience/springboard/project/", sep="")
setwd(DIR)
df<- read.table(paste(DIR, "MergeDataSet.csv", sep=""), sep=",", header=TRUE)
ldf <- tbl_df(df)
caption<-labs(caption="Based on the-numbers.com")
```


## Overall Trend for Number of Movies

```{r echo=FALSE, message=FALSE}
yrsum<-ldf %>% group_by(Year) %>% summarise(n())
p<-ggplot(yrsum, aes(x=Year, y=`n()`)) + geom_bar(stat="identity", width = 1, fill="steelblue") + theme_minimal() +
  labs(title="Number of Movies by Year") + labs(x="Year") + labs(y="Total Number of Movies") + caption
print(p)
```

## Overall Trend of Movies by Genre

```{r echo=FALSE, message=FALSE}
category<-ldf %>% group_by(Genre) %>% summarise(n())

p<-ggplot(category, aes(x=Genre, y=`n()`)) + geom_bar(stat="identity", width = 1, fill="steelblue") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  labs(title="Number of Movies by Genre") + labs(x="Genre") + labs(y="Total Number of Movies") + caption
print(p)
```


##Model Prediction Genre="Drama" 

```{r}
train_data <- tbl_df(df)
genre<-train_data %>% group_by(Year, Genre) %>% summarise(n())
drama <- subset(genre, Genre=="Drama")
drama <- subset(drama, Year<2018)

model1 <- lm(drama$`n()`~Year, data=drama)
mean.num_of_movie=mean(genre$`n()`, na.rm=T)

p<-ggplot(drama, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Drama") + labs(x="Year") +
          labs(y="Number of Movies(Drama)") + caption

print(p)
```

## Model Prediction Genre="Action" 

```{r}
action <- subset(genre, Genre=="Action")
action <- subset(action, Year < 2018)
model1 <- lm(action$`n()`~Year, data=action)
mean.num_of_movie=mean(action$`n()`, na.rm=T)

p<-ggplot(action, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Action") + labs(x="Year") +
          labs(y="Number of Movies(Action)") + caption

print(p)
```


## Model Prediction Genre="Adventure"

```{r}
adven <- subset(genre, Genre=="Adventure")
adven <- subset(adven, Year < 2018)

model1 <- lm(adven$`n()`~Year, data=adven)
mean.num_of_movie=mean(adven$`n()`, na.rm=T)

p<-ggplot(adven, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Adventure") + labs(x="Year") +
          labs(y="Number of Movies(Adventure)") + caption

print(p)
```


## Model Prediction Genre="Comedy"

```{r}
comedy <- subset(genre, Genre=="Comedy")
comedy <- subset(comedy, Year < 2018)

model1 <- lm(comedy$`n()`~Year, data=comedy)
mean.num_of_movie=mean(comedy$`n()`, na.rm=T)

p<-ggplot(comedy, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Comedy") + labs(x="Year") +
          labs(y="Number of Movies(Comedy)") + caption

print(p)
```


##  Model Prediction Genre="Horror"

```{r}
horror <- subset(genre, Genre=="Horror")
horror <- subset(horror, Year < 2018)

model1 <- lm(horror$`n()`~Year, data=horror)
mean.num_of_movie=mean(horror$`n()`, na.rm=T)

p<-ggplot(horror, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Horror") + labs(x="Year") +
          labs(y="Number of Movies(Horror)") + caption

print(p)
```


##Model Prediction Genre="Western"

```{r}
western <- subset(genre, Genre=="Western")
western <- subset(western, Year < 2018)

model1 <- lm(western$`n()`~Year, data=western)
mean.num_of_movie=mean(western$`n()`, na.rm=T)

p<-ggplot(western, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Western") + labs(x="Year") +
          labs(y="Number of Movies(Western)") + caption

print(p)
```


##Model Prediction Genre="Thriller/Suspense"

```{r}
thriller <- subset(genre, Genre=="Thriller/Suspense")
thriller <- subset(thriller, Year < 2018)

model1 <- lm(thriller$`n()`~Year, data=thriller)
mean.num_of_movie=mean(thriller$`n()`, na.rm=T)

p<-ggplot(thriller, aes(x=Year, y=`n()`)) + geom_point() + 
  geom_hline(yintercept=mean.num_of_movie, color="green") + 
  geom_abline(intercept=model1$coefficients[1],
          slope=model1$coefficients[2], color="red") + 
          stat_smooth(method="loess", formula = y ~ x, size=1) +
          labs(title="Genre=Thriller/Suspense") + labs(x="Year") +
          labs(y="Number of Movies(Thriller/Suspense)") + caption

print(p)
```


## Production Budget Trend
```{r echo=FALSE, message=FALSE}
pbudget<-ldf %>% group_by(Year, ProductionBudget) %>% summarise(n())
pbudget$ProductionBudget <- as.numeric(gsub('[$,]', '', pbudget$ProductionBudget))
aggrP<-aggregate(pbudget$ProductionBudget, by=list(Year=pbudget$Year), FUN=sum, na.rm=T)

aggrP<-subset(aggrP, aggrP$Year < 2018)

p<-ggplot(aggrP, aes(x=aggrP$Year, y=aggrP$x)) + 
  geom_bar(stat="identity", width = 0.5, fill="steelblue") + theme_minimal() +
  labs(title="Total Production Budget By Year") + labs(x="Year") + labs(y="Total Production Budget") + caption

print(p)
```

## Domestic Box-Office Collection Trend
```{r echo=FALSE, message=FALSE}
dbudget<-ldf %>% group_by(Year, DomesticBox.Officeto.Date) %>% summarise(n())
dbudget$DomesticBox.Officeto.Date <- as.numeric(gsub('[$,]', '', dbudget$DomesticBox.Officeto.Date))

aggrD<-aggregate(dbudget$DomesticBox.Officeto.Date, by=list(Year=dbudget$Year), FUN=sum, na.rm=T)

aggrD<-subset(aggrD, aggrD$Year < 2018)


p<-ggplot(aggrD, aes(x=aggrD$Year, y=aggrD$x)) + 
  geom_bar(stat="identity", width = 0.5, fill="steelblue") + theme_minimal() +
  labs(title="Domestic Box-Office Collection By Year") + labs(x="Year") + labs(y="Domestic Box-Office Collection") + caption

print(p)
```

##Model Prediction for Production Budget

```{r}
mean.pbudget<-mean(aggrP$x, na.rm=T)
model1 <- lm(aggrP$x~Year, data=aggrP)

p<-ggplot(aggrP, aes(x=aggrP$Year, y=aggrP$x)) + geom_point() + 
  geom_hline(yintercept=mean.pbudget, color="green") +
  geom_abline(intercept=model1$coefficients[1], slope=model1$coefficients[2], color="red") +
  stat_smooth(method="loess", formula = y ~ x, size=1) + 
  labs(title="Production Budget By Year") + labs(x="Year") + labs(y="Production Budget") + caption

print(p)
```

##Model Prediction for Domestic Box-Office Collection

```{r}
mean.pbudget<-mean(aggrD$x, na.rm=T)
model1 <- lm(aggrD$x~Year, data=aggrD)

p<-ggplot(aggrD, aes(x=aggrD$Year, y=aggrD$x)) + geom_point() + 
  geom_hline(yintercept=mean.pbudget, color="green") +
  geom_abline(intercept=model1$coefficients[1], slope=model1$coefficients[2], color="red") +
  stat_smooth(method="loess", formula = y ~ x, size=1) + 
    labs(title="Domestic Box-Office Collection By Year") + labs(x="Year") + labs(y="Domestic Box-Office Collection") + caption


print(p)
```